Modelling the gas kinematics of an atypical Lyman-alpha emitting compact dwarf galaxy

### 2017-10-04 paper/paper.tex
latest

Motivated by observations of other CDGs
  that show gas kinematics ranging from pure rotation and low velocity
dispersion to high velocity dispersion without a clear rotation pattern
\citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
study to explain \tol's \lya emission features under two physical
conditions for the interstellar medium: multiphase outflows and pure rotation.

@@

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, 
  with the minimum $\chi^2/d.o.f.=11.7$. {\bf This relatively high value
    could be interpreted as low statistical significance.
However, we stress once more that this is the first time that the main
features of \tol\ can be reproduced, making this model an useful tool
to guide the interpretation of complex observational data.}

@@

Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial sampling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine Blue Compact Galaxies (BCGs) to produce two-dimensional maps of the
continuum and prominent emission lines to finally compute velocity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms.

@@

In this paper we presented two kinematic models that independently
reproduce the so far unexplained observational features of \tol's
\lya emission line.
One model is based on a multiphase ISM with random clump motions and
the other on gas bulk solid body rotation. 
It is the first time that an observed \lya profile can be fully
reproduced by either of these two kinematic conditions.
Our findings highlight the importance of including multiphase and/or
rotation conditions as kinematic features to model the \lya line.

@@

\bibliographystyle{mnras}
%\bibliography{references}
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

@@

\bibitem[\protect\citeauthoryear{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{2017}]{2017A&A...600A.125C}
{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017, \mn@doi [\aap]
  {10.1051/0004-6361/201629681}, \href
  {http://adsabs.harvard.edu/abs/2017A%26A...600A.125C} {600, A125}

@@

\bibitem[Dijkstra et al.(2006)]{2006ApJ...649...14D} Dijkstra, M., Haiman, Z., \& Spaans, M.\ 2006, \apj, 649, 14

@@

>>>>

Motivated by observations of other CDGs
  that show gas kinematics ranging from pure rotation and low velocity
dispersion to high velocity dispersion without a clear rotation pattern
\citep{2015A&A...577A..21C,2017arXiv170809407C,2017A&A...600A.125C}
we perform here a new study to explain \tol's \lya emission features under two physical
conditions for the interstellar medium: multiphase outflows and pure rotation.

@@

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, 
  with the minimum $\chi^2/d.o.f.=11.7$. {\bf This relatively high value
    for the reduced $\chi^2$ could be interpreted as low statistical
    significance. 
However, we stress once more that the is the first time that the main
features of \tol\ can be reproduced, making this model an useful tool
to guide the interpretation of complex observational data. 
These results certainly open up the path to future searches to
construct new models.}

@@

Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017arXiv170809407C,2017A&A...600A.125C}.
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial sampling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine Blue Compact Galaxies (BCGs) to produce two-dimensional maps of the
continuum and prominent emission lines to finally compute velocity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms.

@@

In this paper we presented two kinematic models that independently
reproduce the so far unexplained observational features of \tol's
\lya emission line.
One model is based on a multiphase ISM with random clump motions and
the other on gas bulk solid body rotation. 
It is the first time that an observed \lya profile can be 
reproduced by either of these two kinematic conditions.
Our findings highlight the importance of including multiphase and/or
rotation conditions as kinematic features to model the \lya line.

@@

\bibliographystyle{mnras}
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

@@

\bibitem[\protect\citeauthoryear{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{2017a}]{2017arXiv170809407C}
{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017a, preprint, \href
  {http://adsabs.harvard.edu/abs/2017arXiv170809407C} {} (\mn@eprint {arXiv}
  {1708.09407})

\bibitem[\protect\citeauthoryear{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
  {Gonz{\'a}lez-P{\'e}rez}}{2017b}]{2017A&A...600A.125C}
{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017b, \mn@doi [\aap]
  {10.1051/0004-6361/201629681}, \href
  {http://adsabs.harvard.edu/abs/2017A%26A...600A.125C} {600, A125}

@@

@@

%\bibliography{references}
